Nail: A practical interface generator for data formats

### 2014-05-01 paper/osdi14/relwk.tex
checkpoint relwk

\XXX[Parsifal at langsec '14]
\paragraph{Parsers}

Generating parsers and generators from an executable specification
is the core concept of Interface Generators, e.g. in CORBA or more
recently~\cite{varda2008}. However, while interface generators work
very well for existing grammars, they do not allow full control over the
format of the output, so cannot be used to implement legacy protocols.
Very related work has been done at Bell Labs with the PacketTypes
system~\cite{mccann2000packet}, however PacketTypes works only as a
parser, not as an output generator and does not support the expressive
power of parsing expression grammars (PEGs), but rather implements a
C-like structure model enhanced with  length fields and
constraints. PacketTypes cannot handle complicated encodings such as  compressed data.

>>>>

\XXX[Parsifal at langsec '14]

\paragraph{Parsers.}

Generating parsers and generators from an executable specification is the
core concept of interface generators, such as CORBA~\cite{omg:corba},
XDR~\cite{rfc:1832}, or Protocol Buffers~\cite{varda2008}.  However,
while interface generators work well for defining new protocols, they
do not provide full control over the data format, and therefore cannot
be used to implement existing protocols and data formats.

Closely related work has been done at Bell Labs with the PacketTypes
system~\cite{mccann2000packet}.  However, PacketTypes works only as a
parser, not as an output generator, and does not support the expressive
power of parsing expression grammars (PEGs), but rather implements a
C-like structure model enhanced with length fields and constraints.
PacketTypes also cannot handle complicated encodings such as compressed
data, which are supported by Nail's stream transforms.
